A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Additional Methods

### 2019-06-10 writeUp/supplementary_materials_methods.tex
Trained neural network for longer
Started to write up methods

>>>>

\section{Detinova parity analysis}
\cite{massey2016global} provide a global database for bionomic quantities for the dominant vector species of malaria. In this database, there are

\cite{detinova1962age} provided an alternative approach to estimate the lifespan of individual specimens, based on sampling the parous rate in a population (the proportion of adult females that have laid eggs) by separating parous from nulliparous females. In what follows, we follow the derivation given by \cite{davidson1954estimation}, to determine an expression for the proportion of nulliparous mosquitoes in terms of the gonotrophic cycle length $G$, here assumed the same for each cycle subsequent to an adult emerging. If a constant daily survival rate $p$ is assumed, the proportion of emerging adults surviving to become parous is $p^G$. If the rate of recruitment into the adult classes is constant over time, the proportion of nulliparous mosquitoes is,
%
\begin{equation}\label{eq:detinova}
\begin{aligned}
\mathbb{n} &= \frac{p^G}{p^G + p^{2G} + p^{3G} + \cdots}\\
&= p^G / \frac{p^G}{1-p^G}\\
&= 1-p^G.
\end{aligned}
\end{equation}
%
The daily survival rate can hence be calculated by inverting eq. (\ref{eq:detinova}): $p = \sqrt[G]{\mathcal{P}}$, where $\mathcal{P}=1-\mathbb{n}$ is the proportion parous sampled from the population.
